---
title: "Survey information"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Survey information}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message = FALSE}
library(fishyplots)
library(dplyr)
```

The survey_table function creates a tile plot with labels to represent the number and type of samples taken from each region yearly. First, load compatible datasets from the package:
```{r}
# Pull biological survey data
data("nwfsc_bio")
data("afsc_bio")
data("pbs_bio")
all_data <- bind_rows(afsc_bio, nwfsc_bio, pbs_bio)
```

The function takes a biological dataset and a species common or scientific name.
```{r}
head(unique(all_data$common_name))
head(unique(all_data$scientific_name))
```

The optional argument `form` controls the structure of the output. The default, `form = 2` outputs a ggplot object. Alternatively, `form = 1` outputs a completed tibble of the same information. 
```{r}
survey_table(data = all_data,
             species = "arrowtooth flounder",
             form = 2)
survey_table(data = all_data,
             species = "arrowtooth flounder",
             form = 1)
```
