---
title: "Age and length frequency"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Age and length frequency}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

First, load relevant libraries and grab the biological datasets in the fishyplots package.

```{r setup, message = FALSE}
library(fishyplots)
library(dplyr)
```

```{r}
data("nwfsc_bio")
data("afsc_bio")
data("pbs_bio")
all_data <- bind_rows(afsc_bio, nwfsc_bio, pbs_bio)
```

This function takes in any number of subregions and 1 species (although note that not all species occur in all regions).
```{r}
unique(all_data$survey)
head(unique(all_data$common_name))
```

Once you have chosen your desired region(s) and species, you can call the functions. Since some species have limited age data, some of the facets in the age frequency plot may be blank.
```{r, warning = FALSE}
age_frequency(all_data, c("PBS", "NWFSC", "AK BSAI", "AK GULF"), "arrowtooth flounder")

length_frequency(all_data, c("PBS", "NWFSC", "AK BSAI", "AK GULF"), "arrowtooth flounder")
```

