---
title: "Mapping density"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Mapping density}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5,
  fig.align = "center",
  dpi = 100
)
```

Density prediction data is stored in the fishyplots package. There are three data frames for each region, which we can combine with `bind_rows` from `dplyr`.
```{r setup, message = FALSE}
# library(fishyplots)
# library(dplyr)
```

```{r}
# data(predictions_afsc)
# data(predictions_pbs)
# data(predictions_nwfsc)
# data <- bind_rows(predictions_afsc, predictions_pbs, predictions_nwfsc)
```

The function takes in these predictions, specified region(s), and 1 species. For instance, we can take a look at arrowtooth flounder densities in all regions. Note that if you select all regions but a species does not occur in all of them, empty base maps will still show up.

```{r, warning = FALSE, fig.height = 12}
#fishmap(data, c("AK BSAI", "AK GULF", "PBS", "NWFSC"), "arrowtooth flounder")
```

Alternatively, you may just want to look at one region.

```{r, warning = FALSE}
#fishmap(data, "PBS", "dover sole")
```

