---
title: "length_weight"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{length_weight}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message = FALSE}
library(fishyplots)
```

This function plots the data and prediction lines for length-weight relationships of a given species in a given dataset. Compatible biological datasets should first be loaded, :

```{r}
# Pull biological survey data
  #individual bio datasets
data(nwfsc_bio)
data(pbs_bio)
data(afsc_bio)
bsai_bio <- afsc_bio |> filter(survey == "AK BSAI")
gulf_bio <- afsc_bio |> filter(survey == "AK GULF")
  #to view all
all_data <- bind_rows(afsc_bio, nwfsc_bio, pbs_bio)
```

The prediction dataset generated from the model fits are called within the function. The function takes a biological dataset and the common or scientific name of a species.

```{r}
head(unique(all_data$common_name))
head(unique(all_data$scientific_name))
```

Input one of the biological datasets to see plots of input species data for that region/survey. If given data with more than one survey present, facet_wrap will present plot windows for all 4 possible surveys. The argument `subset` defaults TRUE to plot a random subset of 10000 points per dataset for plotting speed. To see all available data points, set as FALSE.

```{r}
length_weight(data = all.data,
              species = "arrowtooth flounder",
              subset = TRUE)
```
